Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-03-18 bbbq_article.tex
First decent conclusion section

>>>>

% \paragraph{Over-presentation in vivo in MHC-I is robust}

We confirm that 1.4\% of epitopes that are naturally presented on MHC-I 
can be mapped to stem from a TMH. Additionally, this 
prediction is robust, as it holds for two TMH prediction tools, 
as shown by table \ref{tab:elution}).

% \paragraph{Over-presentation in vivo in MHC-II is robust}

We predict that also MHC-II presents epitopes derived from TMHs
in vivo, as we find that 3.9-4.0\% of sequenced epitopes
can be uniquely traced onto a human reference 
proteome (also shown in table \ref{tab:elution}).

% \paragraph{Over-presentation in silico}

Not only do we predict that MHC-I and MHC-II TMH-derived epitopes 
are presented in vivo, we conclude that these are additionally
presented more often than expected chance 
alone (figures \ref{fig:1} and \ref{fig:2}).
This in silico finding is a general pattern 
that persists in both MHC-I and MHC-II, 
for humans and two pathogens.

% \paragraph{Evolutionary conservation}

We conclude that mutations are more likely to occur
in soluble regions of proteins, than in TMHs.
When selecting SNPs at random, per 1000 SNPs found in a soluble domain, 
one finds on average 918 SNPs in TMHs.
This effect is present in TMPs with two or more TMHs, 
but not in single-spanners.
